\documentclass{eric_cv}

\setname{Eric Moses}{Ngigi}
\setaddress{Nairobi/Kenya}
\setmobile{+254 725 682 601}
\setmail{ericmosesngigi@gmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/erikngigi-dev} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/ErikNgigi} %you can play with color of the template (red is also nice..)
\setwebsite{https:erikngigi.github.io}
\setthemecolor{red} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
\setcompanyname{Andela}
\setcontactperson{Mr.Brown}
\setclaimedposition{Front-End Web Developer} 
\coverletter{ %
I am writing today to express my interest in the Junior Front-End Web Developer opportunity with Andela that I read about on twitter.com on July 1st, 2019.

I was particularly excited to read about this opening because I have been following the success of Andela for quite some time. I recently installed your latest grocery shopping app, and I am a big fan! It would be very fulfilling to be part of a company whose products I love and use everyday.

In considering me for the developer opportunity, Andela would benefit from my skills in responsive web design, as well as my experience learning the latest techniques in HTML, CSS, and JavaScript. I recently did a website overhaul for a local business using just the skills you are asking for. You can check out the link to the website on my resume. In order to keep up with the continually evolving set of tools available to developers, I am continually learning and refining my technical skills.

In addition to my technical skills, I bring along professional work experience in a business setting where I have had to learn new systems quickly, collaborate across many different departments, and communicate decisions and policies to multiple stakeholders.

I appreciate your consideration. I look forward to hearing from you soon!
}
%Footnote
\createfootnote
\end{document}
